A Fast and Tight Heuristic for A* in Road Networks

### 2021-01-21 paper/ch_potentials.tex
related work

% A lot of research focuses on the inflexible setting, i.e., the special case where $w_q = w_\ell$.
% In this setting, mostly hierarchical approaches dominate in terms of running time~\cite{bdgmpsww-rptn-16}.
% A well-known hierarchical technique are Contraction Hierarchies (CH)~\cite{gssv-erlrn-12}.

There is a lot of work that extends hierarchical speed-up techniques to more complex settings.
\todo{cite overview}
% For example, in~\cite{fns-opca-14,gks-rpfof-10} multi-criteria optimization is studied.
MLD/CRP~\cite{dgpw-crprn-13} was developed to allow exchanging weights in reasonable time.
This enable user preferences and live traffic.
MLD/CRP also supports turn costs.
Integrating traffic predictions into CRP was studied in~\cite{bdpw-dtdrp-16}.
In~\cite{dsw-cch-15}, CH is extended to Customizable CH (CCH), which also supports exchanging weights and thus supporting user preferences and live traffic.
CH is extended to support turn costs in~\cite{gv-errnt-11}, CCH in~\cite{bwzz-cchtc-20}.
Traffic predictions are combined with CH in~\cite{swz-sfert-20,bgsv-mtdtt-13}.
\todo{improve! and discuss hierarchical extensions and what they achieve and their difficulties in more details}
\todo{cite traffic aware routing}
Specialized variants for electric vehicle routing are developed in~\cite{DBLP:journals/algorithmica/BaumDPSWZ20,DBLP:conf/aaai/EisnerFS11}.
While these works show that it is possible to extend hierarchical approaches, they also show that it is non-trivial.
Further, in every setting the flexibility available at query time is fairly limited.
Combining all these hierarchical extensions is an unsolved problem.
%
CH-Potentials is not the first work to combine hierarchical approaches and A*~\cite{bdsssw-chgds-10,gkw-blwr-07,bdgwz-sfpcs-19}.
However, a lot of past works use A* to accelerate hierarchical approaches even further and loose A*'s flexibility.
%

>>>>

There is a lot of work that extends hierarchical speed-up techniques to more complex settings~\cite{bdgmpsww-rptn-16}.
For example, in~\cite{gv-errnt-11} turn information is integrated into CH.
The proposed approach achieves fast queries but preprocessing becomes an order of magnitude slower compared to classical CH.
A considerable amount of research and engineering effort has been put into studying the combination of traffic predictions with CH.
Several papers~\cite{} and an entire dissertation~\cite{} have been published on the subject.
\todo{cite td stuff}
Different techniques with trade-offs regarding exactness, query speed and space consumption were proposed~\cite{bgsv-mtdtt-13}.
Recently, a new approach has been published~\cite{swz-sfert-20} which simultaneously achieves all three goals but only at the cost of considerable implementation complexity.
%
CRP~(Customizable Route Planning)~\cite{dgpw-crprn-13} is an engineered variant of Multi-Level Dijkstra~(MLD)~\cite{swz-umlgt-02} which was developed to allow updating weights without invalidating the entire preprocessing.
For this, a faster, second preprocessing phase is introduced which can be run regularly to update weights.
In theory, this enables the integration of live traffic and user preferences.
In practice, live traffic feed data is imperfect.
Computing ``good'' routes without undesired detours due to artifacts in the data requires additional algorithmic extensions~\cite{}.
\todo{cite traffic aware routing}
CRP also supports turn costs.
Integrating traffic predictions into CRP was studied in~\cite{bdpw-dtdrp-16}.
However, on continental sized networks, the proposed approach can only compute approximate shortest distances (rather than paths).
%
In~\cite{dsw-cch-15}, CH is extended to Customizable CH (CCH).
CCH also has a second preprocessing phase where weights can be altered.
Supporting turn costs in CCH was studied in~\cite{bwzz-cchtc-20}.
Turn integration still causes a slowdown of at least factor three to the second preprocessing phase.
Other extensions studied include electric vehicle routing~\cite{DBLP:journals/algorithmica/BaumDPSWZ20,DBLP:conf/aaai/EisnerFS11} or multi-criteria optimization~\cite{fns-opca-14,gks-rpfof-10}.
%
While these works show that it is possible to extend hierarchical approaches, they also show that it is non-trivial.
Further, in every setting the flexibility available at query time is fairly limited.
Combining these hierarchical extensions is an unsolved problem.

CH-Potentials is not the first work to combine hierarchical approaches and A*~\cite{bdsssw-chgds-10,gkw-blwr-07,bdgwz-sfpcs-19}.
However, a lot of past works use A* to accelerate hierarchical approaches even further and loose A*'s flexibility.
%
